Functory: Distributed Computing for the Common Man\thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2010-10-11 doc/report/main.tex
*** empty log message ***

\item \textbf{Master and workers are different programs, not even
    compiled with the same version of \Ocaml:} we can no
  longer use marshaling, so the
  \ocaml{compute} function is split into two monomorphic functions
  over strings:%
\vspace{-1em}
\begin{ocaml}
val Worker.compute : (string -> string) -> unit -> unit
val Master.compute : 
  (string * 'c -> string -> (string * 'c) list) -> 
  (string * 'c) list -> unit
\end{ocaml}
  Note that the second component of each task is still polymorphic (of
  type \ocaml{'c} here), since it is local to the master.
\end{enumerate}

@@

Though the ability to run the same executable helps a lot in deploying
the program in different machines, it comes at a small price. Since
the worker is not getting into the user code, closures which are
transmitted from the master can not refer to global variables in the
user code. Indeed, the initialization code for these global variables
is never reached on the worker side. For instance, the Mandelbrot set
example could be written as follows:
\begin{ocaml}
  let max_iterations = 200
  let worker (xmi, xma, ymi, yma, w, h) =
    ... draw sub-image using max_iterations ...
\end{ocaml}
That is, the global function \of{worker} makes use of the global
variable \of{max_iterations}. The worker gets the function to compute
from the master, namely the closure corresponding to function
\of{worker} in that case, but on the worker side the initialization of
\of{max_iterations} is never executed.

@@

% TODO : explain the new derived API

\paragraph{\of{Mono}.}

% TODO

% \bigskip

>>>>

\item \textbf{Master and workers are different programs, not even
    compiled with the same version of \Ocaml:} we can no
  longer use marshaling, so the
  \ocaml{compute} function is split into two monomorphic functions
  over strings:%
\vspace{-1em}
\begin{ocaml}
val Worker.compute : (string -> string) -> unit -> unit
val Master.compute : 
  (string * 'c -> string -> (string * 'c) list) -> 
  (string * 'c) list -> unit
\end{ocaml}
\end{enumerate}

@@

Though the ability to run the same executable helps a lot in deploying
the program in different machines, it comes at a small price. Since
the worker is not getting into the user code, closures which are
transmitted from the master cannot refer to global variables in the
user code. Indeed, the initialization code for these global variables
is never reached on the worker side. For instance, the Mandelbrot set
example could be written as follows:
\begin{ocaml}
  let max_iterations = 200
  let worker (xmi, xma, ymi, yma, w, h) =
    ... draw sub-image using max_iterations ...
\end{ocaml}
That is, the global function \of{worker} makes use of the global
variable \of{max_iterations}. The worker gets the function to compute
from the master, namely the closure corresponding to function
\of{worker} in that case, but on the worker side the initialization of
\of{max_iterations} is never executed.

@@

The derived API presented in Section~\ref{sec:derived} is adapted to
deal with the absence of closures. Exactly as the \of{compute}
function, each API now takes two forms, one for the master and another
for the workers. For example, \of{map_fold_ac} takes the following
forms.
\begin{ocaml}
  Worker.map_fold_ac : map:('a -> 'b) -> fold:('b -> 'b -> 'b) -> unit -> unit
  Master.map_fold_ac : 'b -> 'a list -> 'b
\end{ocaml}
It is the responsibility of the user to ensure type consistency between
master and workers.

\paragraph{\of{Mono}.} When master and workers are compiled using
different versions of \Ocaml, we can no longer use marshaling. 
As in the previous case, we split \of{compute} into two functions, one
for master and one for workers. In addition, values transmitted over
the network can only be strings. The signature thus takes the
following form.
\begin{ocaml}
  Worker.compute : (string -> string) -> unit -> unit
  Master.compute : master:(string * 'c -> string -> (string * 'c) list) -> 
                  (string * 'c) list -> unit
\end{ocaml}
Any other datatype for tasks should be encoded to/from strings. This
conversion is left to the user.
Note that the second component of each task is still polymorphic (of
type \of{'c} here), since it is local to the master.
